### 2012-10-16 fermi/tevcat/paper/sections/abstract.tex
update

Since its launch, the \emph{Fermi} satellite has firmly identified 7 pulsar wind nebulae (PWNe) plus a large number of candidates, all powered by young and energetic pulsars. Furthermore, PWNe are the most populous class in the TeV energy range followed by the unidentified sources (UNID). Using 45 months of Fermi--LAT data, we looked around the position of 56 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts. For each of them we derived a $\gamma$--ray flux or an upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT) above 10~GeV.

The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the gamma-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.

>>>>

Since its launch, the \emph{Fermi} satellite has firmly identified 7 pulsar wind nebulae (PWNe) plus a large number of candidates, all powered by young and energetic pulsars. Furthermore, PWNe are the most populous class in the TeV energy range followed by the unidentified sources (UNID). Using 45 months of Fermi--LAT data, we looked around the position of 58 TeV sources to bring new constraints on the models and new clues on the nature of sources without counterparts. For each of them we derived a $\gamma$--ray flux or an upper limit (when the TeV source is not detected at GeV energies by the \emph{Fermi}--LAT) above 10~GeV.

The wealth of multi-wavelength data available and the new results provided by \emph{Fermi}--LAT is an extraordinary opportunity to constrain the origin of the $\gamma$-ray emission of the large sample of UNID and the radiative processes taking place in known PWNe.

### 2012-10-16 fermi/tevcat/paper/sections/introduction.tex
update

Multi-wavelength observations are essential to constrain the emission mechanisms occurring in these sources and identify their nature. The Large Area Telescope (LAT) aboard the \emph{Fermi} Gamma-Ray Space Telescope (\emph{Fermi}) is especially useful in this context. Covering the energy range from $\sim$ 100 MeV to more than 300 GeV, the LAT provides a precise view of the $\gamma$-ray sky. With 2 years of observations, the \emph{Fermi}--LAT Second Catalog \citep{2012ApJS..199...31N} already contains 1873 sources, 1397 being identified and 576 without counterparts.

@@

The motivation of this work is to bring new constraints on already known PWNe and to look for new candidates among the unidentified TeV sources.  A search for gamma-ray emission in the off-pulse window of the $\gamma$-ray detected pulsars, updating the method proposed in \cite{2011ApJ...726...35A}, will be presented in \textbf{cite 2PC}. The strategy presented in our work (this paper) is closer to \cite{2010AA...518A...8T} in the sense that we analyzed the \emph{Fermi}-LAT data around already known potential PWNe.

The sources included in our search were detected by H.E.S.S., VERITAS, MAGIC and MILAGRO. H.E.S.S. \citep{2006AA...457..899A} is composed of four telescopes observing the very high energy (VHE) sky from 0.1 to 100 TeV with a mean point spread function (PSF) of $\sim$0.1$\degr$ for a point--source sensitivity around 1$\%$ of the Crab flux above 200 GeV for 25 hours of observations. The four telescopes of VERITAS \citep{2002APh....17..221W} detect the $\sim$ 0.1 to 30 TeV $\gamma$-rays with a sensitivity of 1$\%$ of the Crab in less than 30 hours and an angular resolution lower than 0.1$\degr$ at 1 TeV. MAGIC \citep{2012APh....35..435A} consists of two telescopes observing from $\sim$ 50 GeV to several tens of TeV with a sensitivity of $\sim$ 0.8$\%$ of the Crab nebula flux above 300 GeV with a $\sim$ 0.1$\degr$ PSF. MILAGRO \citep{2007ApJ...658L..33A} is a water $\breve{C}$erenkov detector with a large field of view (FoV) of $\sim$2sr and a $\sim$ 0.45$\degr$ angular resolution observing $\gamma$-rays from $\sim$ 1 to 100 TeV. 
%{\bf {\color{red} Manque les references}}

@@

Starting from the TeV catalog website \footnote{http://tevcat.uchicago.edu/}, which summarizes all sources detected at TeV energies, we established a list of sources possibly associated to PWNe (Section 3), that we studied using the method and the tools described in Section 4. The spatial and spectral results (Section 5) will be presented in the context of a population study (Section 6) before discussing the case one by one (Section 7). \textbf{a remoduler une fois le reste fait.}

>>>>

Multi-wavelength observations are essential to constrain the emission mechanisms occurring in these sources and identify their nature. The Large Area Telescope (LAT) aboard the \emph{Fermi} Gamma-ray Space Telescope (\emph{Fermi}) is especially useful in this context. Covering the energy range from $\sim$ 100 MeV to more than 300 GeV, the LAT provides a precise view of the $\gamma$-ray sky. With 2 years of observations, the \emph{Fermi}--LAT Second Catalog \citep{2012ApJS..199...31N} already contains 1873 sources, 1397 being identified and 576 without counterparts.

@@

The motivation of this work is to bring new constraints on already known PWNe and to look for new candidates among the unidentified TeV sources. A search for $\gamma$-ray emission in the off-pulse window of the $\gamma$-ray detected pulsars, updating the method proposed in \cite{2011ApJ...726...35A}, will be presented in \cite{2PC}. The strategy presented in our work (this paper) is closer to \cite{2010AA...518A...8T} in the sense that we analyzed the \emph{Fermi}-LAT data around already known potential PWNe.

The sources included in our search were detected by H.E.S.S., VERITAS, MAGIC and MILAGRO. H.E.S.S. \citep{2006AA...457..899A} is composed of four telescopes observing the very high energy (VHE) sky from 0.1 to 100 TeV with a mean point spread function (PSF) of $\sim$0.1$\degr$ for a point--source sensitivity around 1$\%$ of the Crab flux above 200 GeV for 25 hours of observations. The four telescopes of VERITAS \citep{2002APh....17..221W} detect the $\sim$ 0.1 to 30 TeV $\gamma$-rays with a sensitivity of 1$\%$ of the Crab in less than 30 hours and an angular resolution lower than 0.1$\degr$ at 1 TeV. MAGIC \citep{2012APh....35..435A} consists of two telescopes observing from $\sim$ 50 GeV to several tens of TeV with a sensitivity of $\sim$ 0.8$\%$ of the Crab nebula flux above 300 GeV with a $\sim$ 0.1$\degr$ PSF. MILAGRO \citep{2004ApJ...608..680A} is a water $\breve{C}$erenkov detector with a large field of view (FoV) of $\sim$2sr and a $\sim$ 0.45$\degr$ angular resolution observing $\gamma$-rays from $\sim$ 1 to 100 TeV. 
%{\bf {\color{red} Manque les references}}

@@

Starting from the TeV catalog website \footnote{http://tevcat.uchicago.edu/}, which summarizes all sources detected at TeV energies, we established a list of sources possibly associated to PWNe (Section 3), that we studied using the method and the tools described in Section 4. The most interesting cases as well as the spatial and spectral results will be discussed (Section 5) before being presented in the context of a complete population study (Section \ref{discussion}).

%will be presented in the context of a population study (Section 6) before discussing the case one by one (Section 7). \textbf{a remoduler une fois le reste fait.}

### 2012-10-16 fermi/tevcat/paper/sections/lat_description_and_observations.tex
update

The following analysis was performed using 45 months of data collected from August 4, 2008 to Mai 18, 2012 (MET : 239557440--356439741) within a $7$\degr $\times 7\degr$ square (see section 4) around the position of the TeV source aligned with Galactic coordinates. We excluded $\gamma$-rays coming from a zenith angle larger than 100$\degr$ because of possible contamination from secondary $\gamma$-rays from the Earth's atmosphere \citep{2009PhRvD..80l2004A}. We used the Pass 7 clean event class that has a substantial reduction in instrumental background above 10 GeV with only a small loss in effective area (compared to the standard event class).

>>>>

The following analysis was performed using 45 months of data collected from August 4, 2008 to April 18, 2012 (MET : 239557440--356439741) within a $7$\degr $\times 7\degr$ square (see section 4) around the position of the TeV source aligned with Galactic coordinates. We excluded $\gamma$-rays coming from a zenith angle larger than 100$\degr$ because of possible contamination from secondary $\gamma$-rays from the Earth's atmosphere \citep{2009PhRvD..80l2004A}. We used the Pass 7 clean event class that has a substantial reduction in instrumental background above 10 GeV with only a small loss in effective area (compared to the standard event class).
